How fluid-mechanical erosion creates anisotropic porous media

### 2022-12-14 docs/PhysicsPaper/StokesErosion.tex
NM

>>>>

	\edit{Random configurations of bodies are initialized by sampling a list of the radii from a Chi distribution while enforcing the desired initial porosity. These circular bodies are initially positioned randomly, which typically results in many overlapping bodies. To eliminate overlap, we employ a simulated-annealing algorithm, in which fictitious forces act on the bodies. The force on each body includes a deterministic repulsive component that acts to separate the bodies from one another and from the domain walls along with a stochastic component whose magnitude decreases with time.}
